\bfseries A simple momentum-transport model for sailing

### 2024-08-02 paper/main.tex

In \figref{fig:steady} we show examples of steady sailing, for a wide range of orientations of the keel and sail.
All these examples are shown in the water rest frame.
The boat has four free parameters $(A_\sail,A_\keel,A_{\above},A_{\below})$ all with units of area (or really three independent dimensionless ratios of these four areas).
The values we chose for these four parameters are given in \secref{sec:design} and discussed in detail there.
\begin{figure}[t!]
  \includegraphics[width=\textwidth]{steady.pdf}
  \caption{Visualizations of the boat velocity $\vboat$ for different settings of the orientations of the keel and sail, all presented in the water rest frame.
  The views are top-down; the keel is represented by a thick grey line, the sail is represented by a thin black line, and the wind and boat velocities are represented by black arrows.
  Most of the settings of the keel and sail lead to downwind travel, but a few in the top-left quarter of this grid lead to upwind travel. LEHMAN: HIGHLIGHT THE FRAME WITH THE OPTIMAL ANGLE OF ATTACK IN EACH COLUMN?\label{fig:steady}}
  \figurerule
\end{figure}

>>>>

In \figref{fig:steady} we show examples of steady sailing, for a wide range of orientations of the keel and sail.
All these examples are shown in the water rest frame.
The boat has four free parameters $(A_\sail,A_\keel,A_{\above},A_{\below})$ all with units of area (or really three independent dimensionless ratios of these four areas).
The values we chose for these four parameters are given in \secref{sec:design} and discussed in detail there.
\begin{figure}[t!]
  \includegraphics[width=\textwidth]{steady.pdf}
  \caption{HOGG: THIS CAPTION IS ALL WRONG NOW: ALL PLOTTED VELOCITIES ARE DIFFERENCES. Visualizations of the boat velocity $\vboat$ for different settings of the orientations of the keel and sail, all presented in the water rest frame.
  The views are top-down; the keel is represented by a thick grey line, the sail is represented by a thin black line, and the wind and boat velocities are represented by black arrows.
  Most of the settings of the keel and sail lead to downwind travel, but a few in the top-left quarter of this grid lead to upwind travel. LEHMAN: HIGHLIGHT THE FRAME WITH THE OPTIMAL ANGLE OF ATTACK IN EACH COLUMN?\label{fig:steady}}
  \figurerule
\end{figure}
